A Computational Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-01 paper/paper.tex
addon

\subsection{The right and left TPJ: Prediction error signaling and world semantics}
While the DMN emerges with its midline structures early in development,
the right and left TPJ may become fully integrated into this canonical
network only after birth \citep{doria2010}.
The TPJs are known to have hemispheric differences
according to their cytoarchitectonic borders and gyrification pattern
\citep{seghier2013angular}.
Neuroscientific investigations on hemispheric functional specialization
have highlighted the right versus left cerebral hemisphere as dominant for
attention versus language functions.

>>>>

\subsection{The right and left TPJ: Prediction error signaling and world semantics}
While the DMN emerges with its midline structures early in human development,
the right and left TPJ may become fully integrated into this canonical
network only after birth \citep{doria2010}.
The TPJs are known to have hemispheric differences
according to their cytoarchitectonic borders and gyrification pattern
\citep{seghier2013angular}.
Neuroscientific investigations on hemispheric functional specialization
have highlighted the right versus left cerebral hemisphere as dominant for
attention versus language functions.
